An Experimental Evaluation of Hybrid Vector Search (EA\&B)

### 2025-04-16 VLDB2026/main.tex
Update main.tex

	(2)\textbf{ Evaluation of Attribute Filtering Algorithms.}
	We conduct a systematic evaluation of 13 attribute filtering algorithms on 6 real-world datasets. By analyzing performance under varying numbers of attributes, we reveal the strengths and weaknesses of each method. We further examine their behavior under different attribute distributions and selectivity conditions to assess robustness and adaptability in complex query scenarios. Evaluation metrics include index construction time, index size, peak memory usage, QPS, and search accuracy.

>>>>

	(2)\textbf{ Evaluation of Attribute Filtering Algorithms.}
	We conduct a systematic evaluation of 13 attribute filtering algorithms on 7 real-world datasets. By analyzing performance under varying numbers of attributes, we reveal the strengths and weaknesses of each method. We further examine their behavior under different attribute distributions and selectivity conditions to assess robustness and adaptability in complex query scenarios. Evaluation metrics include index construction time, index size, peak memory usage, QPS, and search accuracy.
